Supplementary materials

### 2018-02-19 publication/supp_info.Rmd
Smaller table text

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
options(xtable.comment = FALSE, 
        xtable.caption.placement = 'bottom',
        booktabs = TRUE)
library(drake)
library(ggplot2)
library(xtable)
library(tidyr)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
options(xtable.comment = FALSE, 
        xtable.caption.placement = 'bottom',
        xtable.size = 'small',
        booktabs = TRUE)
library(drake)
library(ggplot2)
library(xtable)
library(tidyr)
```
